Automated Essay Scoring

### 2018-05-10 paper/acl17-latex/paper.tex
added citations

There is a recent surge in use of deep learning for the task of automated essay scoring.
These models have shown to out perform the traditional models based on hand coded features
and currently have the state of art performance in this task. The current state of art model
is from Taghipour et al. \cite{nea} and the state of art non-neural model is EASE \cite{ease}.
In this paper we explore the performance of deep-learning based systems on real life scenarios. We try to see if their performance is actually better than traditional non-neural based models in qualitative sense.

@@

% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2017}
\bibliography{acl2017}
\bibliographystyle{acl_natbib}

>>>>

Automated essay scoring systems(AES) are used in evaluating and scoring student essays written based on a given prompt. The performance of these systems is assessed by comparing their scores assigned to a set of essays to human-assigned gold-standard scores.
Since the output of AES systems is usually a real valued number, the task is often addressed as a supervised machine learning task.
Recently, there is a lot of development of deep neural models for the task of automated essay scoring.
These models have shown to out perform the traditional models based on hand coded features and currently have the state of art performance in this task. The current state of art model is from Taghipour et al. \cite{nea} and the state of art non-neural model is EASE \cite{ease}.
In this paper we explore the performance of deep-learning based systems on real life scenarios. We try to see if their performance is actually better than traditional non-neural based models in qualitative sense.

@@

% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2017}
\bibliography{paper}
\bibliographystyle{acl_natbib}
